Article Name

### 2021-11-24 elsevier/appendix.Rmd
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

---
output: pdf_document
---
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

@@

Table.\ref{tab:stable} is in Supplementary materials.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:stable}This table again")
```

>>>>

---
output: 
  bookdown::pdf_book: default
  bookdown::word_document2: default  # for cross-references
---
\renewcommand{\thefigure}{S\arabic{figure}}
\setcounter{figure}{0}
\renewcommand{\thetable}{S\arabic{table}}
\setcounter{table}{0}
\renewcommand{\theequation}{S\arabic{equation}}
\setcounter{equation}{0}

# Supplementary materials {#appendix .unnumbered}

@@

Table.\ref{tab:stable} is in Supplementary materials.
```{r, echo=FALSE, warning=FALSE, message=FALSE}
data %>% 
          group_by(supp) %>%
          summarise(median = round(median(len), 3),
                    mean = round(mean(len), 3)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:stable}This table again")
```

### 2021-11-24 elsevier/manuscript.Rmd
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

---
title: Article Name
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  This is the abstract.  
  1. what is the study about?  
  2. what problem does it address?  
  3. how did you conduct the research?  
  4. what were the main findings?  
  5. why is it important?

keywords: "keywordA, keywordB"
journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
#linenumbers: true
numbersections: true
header-includes:
    - \usepackage{setspace}\doublespacing
    - \usepackage{lineno}\linenumbers
csl: harmful-algae.csl
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    includes:  
      in_header: my_header.tex
linkcolor: blue
---
```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(here)
library(kableExtra)
library(tidyverse)

data <- read.csv(here("data", "process", "newdata.csv"))
```

@@

```{r boxplot, echo=FALSE, fig.cap='A boxplot', out.height="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
```

@@

(ref:longcaption) This is a very long caption
```{r 2021, echo=FALSE, fig.cap='(ref:longcaption)', out.width="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "pictures", "2021.png"))
```

## Adding tables {#table}
```{r, echo=FALSE, warning=FALSE, message=FALSE}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

@@

# Results and discussion {#result}
## Use code inline
The maximum tooth length is `r max(data$len)`.

@@

@@

# CRediT authorship contribution statement {#authorship .unnumbered}

# Data availability {#datasharing .unnumbered}

# Declaration of competing interest {#declaration .unnumbered}
The authors declare that they have no known competing financial interests or personal relationships that could have appeared to influence the work reported in this paper.

# Acknowledgements {#thanks .unnumbered}

# Supplementary materials {#appendix .unnumbered}
```{r, child="appendix.Rmd"}

@@

# References {#references .unnumbered}

>>>>

---
title: Article Name
author:
  - name: Author One
    email: one@example.com
    affiliation: a,1
  - name: Author Two
    email: two@example.com
    affiliation: a,b
    footnote: 1
  - name: Author Three
    email: three@example.com
    affiliation: c
    footnote: 2
  - name: Author Four
    email: four@example.com
    affiliation: a
    footnote: 2
address:
  - code: a
    address: Graduate School of Engineering, Nagasaki University, 1-14 Bunkyo-machi, Nagasaki 852-8521, Japan
  - code: b
    address: Department, University, Street, City, State, Zip
  - code: c
    address: Department, University, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
  - text: "^1^Present address: Department, University, Street, City, State, Zip"
abstract: |
  This is the abstract.  
  1. what is the study about?  
  2. what problem does it address?  
  3. how did you conduct the research?  
  4. what were the main findings?  
  5. why is it important?

keywords: "keywordA, keywordB"
journal: "An awesome journal"
date: "`r Sys.Date()`"
bibliography: bibliography.bib
#linenumbers: true
numbersections: true
layout: review      #review=doublespace, preprint=single, 5p=2column
csl: harmful-algae.csl        #download .csl at www.zotero.org/styles
output:
  bookdown::pdf_book:
    base_format: rticles::elsevier_article
    includes:  
      in_header: my_header.tex
  bookdown::word_document2: default  # for cross-references
linkcolor: blue
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)

library(here)
library(tidyverse)
library(kableExtra)
```

```{r}
data <- read.csv(here("data", "process", "newdata.csv"))
```

\newpage

@@

```{r boxplot, fig.cap='A boxplot', out.height="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "figures", "boxplot.pdf"))
```

@@

(ref:longcaption) This is a very long caption
```{r 2021, fig.cap='(ref:longcaption)', out.width="50%", fig.align='center'}
knitr::include_graphics(here::here("results", "pictures", "2021.png"))
```

## Adding tables {#table}
```{r}
data %>% 
          group_by(supp) %>%
          summarise(median = median(len),
                    mean = mean(len)) %>% 
	kable("simple",
	      booktabs = T,
	      col.names = c("Supplement type", 
	      	    	"Median",
	      	    	"Mean"), 
	      align = "cll",
	      caption = "\\label{tab:cooltable}Mean and Median")
```

@@

# Results {#result}
## Use code inline
The maximum tooth length is `r max(data$len)`.

@@

# Discussion {#discussion}

@@

\newpage

```{r, child="interest.Rmd"}

@@

```{r, child="credit.Rmd"}

```{r, child="thanks.Rmd"}

\newpage
# References {#references .unnumbered}
<div id="refs"></div>

\newpage
```{r, child="appendix.Rmd"}

\newpage
```{r, child="highlight.Rmd"}

# Graphical abstract {#graphic .unnumbered}
Delete `eval=FALSE` before run the code chunk

```{r, out.width="50%", fig.align='center', eval=FALSE}
knitr::include_graphics(here("results", "figures", "graphical_abstract.pdf"))
```

\newpage
```{r, child="cover_letter.Rmd"}

```{r, child="response_to_reviewers.Rmd"}

### 2021-11-24 elsevier/manuscript.tex
update `elsevier/`: revised YAML of manuscript.Rmd; add child documents: cover-letter, response-to-reviewer, credit, declaration of competing interest (.docx + .Rmd), acknowledgements, highlight

\documentclass[]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

% Pandoc header
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{setspace}\doublespacing
\usepackage{lineno}\linenumbers
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \title{Article Name}
    \author[Some Institute of Technology]{Alice Anonymous\corref{1}}
   \ead{alice@example.com} 
    \author[Another University]{Bob Security}
   \ead{bob@example.com} 
    \author[Another University]{Cat Memes\corref{2}}
   \ead{cat@example.com} 
    \author[Some Institute of Technology]{Derek Zoolander\corref{2}}
   \ead{derek@example.com} 
      \address[Some Institute of Technology]{Department, Street, City, State, Zip}
    \address[Another University]{Department, Street, City, State, Zip}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}

@@

@@

\section{Results and discussion}\label{result}

@@

@@

\section*{CRediT authorship contribution statement}\label{authorship}
\addcontentsline{toc}{section}{CRediT authorship contribution statement}

\section*{Data availability}\label{datasharing}
\addcontentsline{toc}{section}{Data availability}

\section*{Declaration of competing interest}\label{declaration}
\addcontentsline{toc}{section}{Declaration of competing interest}

@@

@@

@@

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-4}\label{tab:stable}This table
again}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.66333\tabularnewline
VC & 16.5 & 16.96333\tabularnewline
\bottomrule
\end{longtable}

@@

>>>>

\documentclass[review]{elsarticle} %review=doublespace preprint=single 5p=2 column
%%% Begin My package additions %%%%%%%%%%%%%%%%%%%
\usepackage[hyphens]{url}

@@

% Pandoc header
%fix position of table, figure
\usepackage{float}
\let\origfigure\figure
\let\endorigfigure\endfigure
\renewenvironment{figure}[1][2] {
    \expandafter\origfigure\expandafter[H]
} {
    \endorigfigure
}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{multirow}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
\usepackage{threeparttable}
\usepackage{threeparttablex}
\usepackage[normalem]{ulem}
\usepackage{makecell}
\usepackage{xcolor}

@@

  \title{Article Name}
    \author[a,1]{Author One}
   \ead{one@example.com} 
    \author[a,b]{Author Two\corref{1}}
   \ead{two@example.com} 
    \author[c]{Author Three\corref{2}}
   \ead{three@example.com} 
    \author[a]{Author Four\corref{2}}
   \ead{four@example.com} 
      \address[a]{Graduate School of Engineering, Nagasaki University, 1-14 Bunkyo-machi,
Nagasaki 852-8521, Japan}
    \address[b]{Department, University, Street, City, State, Zip}
    \address[c]{Department, University, Street, City, State, Zip}
      \cortext[1]{Corresponding Author}
    \cortext[2]{Equal contribution}
    \cortext[]{\textsuperscript{1}Present address: Department, University, Street,
City, State, Zip}

@@

\newpage

@@

\section{Results}\label{result}

@@

\section{Discussion}\label{discussion}

@@

\newpage

\section*{Declaration of competing interest}\label{interest}
\addcontentsline{toc}{section}{Declaration of competing interest}

@@

\section*{CRediT authorship contribution statement}\label{credit}
\addcontentsline{toc}{section}{CRediT authorship contribution statement}

\textbf{Author One:} Conceptualization, Methodology, Investigation, Data
curation, Formal analysis, Visualization, Writing - Original Draft,
Writing - review \& editing. \textbf{Author Two:} Supervision, Project
administration, Funding acquisition, Conceptualization, Resources,
Writing - Review \& Editing. \textbf{Author Three, Author Four:}
Investigation.

Further information
\href{https://www.elsevier.com/authors/policies-and-guidelines/credit-author-statement}{here}.

@@

This work was supported by \ldots{}

\newpage

\newpage

@@

\begin{longtable}[]{@{}cll@{}}
\caption{\label{tab:unnamed-chunk-11}\label{tab:stable}This table
again}\tabularnewline
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endfirsthead
\toprule
Supplement type & Median & Mean\tabularnewline
\midrule
\endhead
OJ & 22.7 & 20.663\tabularnewline
VC & 16.5 & 16.963\tabularnewline
\bottomrule
\end{longtable}

@@

\newpage

\section*{Highlights}\label{highlight}
\addcontentsline{toc}{section}{Highlights}

Short collection of bullet points: novel results + new methods\\
- submitted: separate editable file -\textgreater{} online submission
system.\\
- file name: `Highlights'\\
- 3 to 5 bullet points (maximum 85 characters, including spaces, per
bullet point)

\section*{Graphical abstract}\label{graphic}
\addcontentsline{toc}{section}{Graphical abstract}

Delete \texttt{eval=FALSE} before run the code chunk

\newpage

\section*{Cover letter}\label{cover-letter}
\addcontentsline{toc}{section}{Cover letter}

\subsubsection*{New submission}\label{new-submission}
\addcontentsline{toc}{subsubsection}{New submission}

Month Day, Year

Dear Dr.~AAA,

I am happy to submit my manuscript, \textbf{article\_name}, for your
consideration at \emph{journal\_name}. This work \emph{do sth
interesting}. The main conclusion is that \emph{sth cool}.

All of the authors have read and approved the paper and it has not been
published previously nor is it being considered by any other
peer-reviewed journal.

The manuscript has also been submitted to bioRxiv as a preprint.

Sincerely,

Author\_name, PhD\\
Professor

\subsubsection*{Resubmissions}\label{resubmissions}
\addcontentsline{toc}{subsubsection}{Resubmissions}

Month Day, Year

Dear Dr.~BBB,

I am happy to resubmit my manuscript, \textbf{article\_name}, for your
reconsideration at \emph{journal\_name}. I am grateful to you and the
reviewers who were very encouraging about the content of the
manuscript.\\
I apologize for taking so long to resubmit.\\
Too many things got in the way over the past few months.

All of the authors have read and approved the paper and it has not been
published previously nor is it being considered by any other
peer-reviewed journal.

The manuscript was previously submitted to bioRxiv as a preprint.

Sincerely,

Author\_name, PhD\\
Professor

\section*{Response to reviewers}\label{response-to-reviewers}
\addcontentsline{toc}{section}{Response to reviewers}

\subsubsection*{Reviewer \#1 (Comments for the
Author):}\label{reviewer-1-comments-for-the-author}
\addcontentsline{toc}{subsubsection}{Reviewer \#1 (Comments for the
Author):}

\textbf{copy the comment of the reviewer here}

\begin{quote}
We have revised the sentence to the following: ``sth you revised''
\end{quote}

\subsubsection*{Reviewer \#2 (Comments for the
Author):}\label{reviewer-2-comments-for-the-author}
\addcontentsline{toc}{subsubsection}{Reviewer \#2 (Comments for the
Author):}

\textbf{copy the comment of the reviewer here}

\begin{quote}
Your response here
\end{quote}

A great example
\href{https://github.com/SchlossLab/Tomkovich_PEG3350_mSphere_2021/blob/master/submission/response_to_reviewers.md}{here}.
